TBD

### 2021-03-18 outputs/paper/paper.Rmd
update

We replicate this paper using R statistical programming language [@citeR]. In particular, we use packages `tidyverse` [@citeTidyverse],  `here` [@citehere], `ggpubr` [@citeggpubr] to manipulate data and packages, `kableExtra` [@citekableExtra] to generate tables, and `ggplot2` [@citeggplot], `ggthemes` [@citeggthemes] to adjust diagrams themes.

@@

```{r fs, echo=FALSE, warning=FALSE,fig.width=4, fig.height=6 }
# more codes are in the scripts (path: scripts/02_feature selection)
FS<- dat%>%
  select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake,exp_2,exp_2_prompt_accuracy,exp_2_after_debrief,exp_2_prompt,Zip,believed_true))%>% na.omit()

>>>>

We replicate this paper using R statistical programming language [@citeR]. In particular, we use packages `tidyverse` [@tidy],  `here` [@citehere], `ggpubr` [@citeggpubr] to manipulate data and packages, `kableExtra` [@citekableExtra] to generate tables, and `ggplot2` [@citeggplot], `ggthemes` [@citeggthemes] to adjust diagrams themes.

@@

```{r fs, echo=FALSE, warning=FALSE,fig.width=10, fig.height=10 }
# more codes are in the scripts (path: scripts/02_feature selection)
FS<- dat%>%
  select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake,exp_2,exp_2_prompt_accuracy,exp_2_after_debrief,exp_2_prompt,Zip,believed_true))%>% na.omit()
